Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-01-22 ms.tex
I added an early MCMC fit to the time series to generate a whole spectrum for 2MASS 0835.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J1821- Automatic Shifting]{
	\includegraphics[width=0.5\textwidth]{specphot_1821_auto_noremovel.pdf}
	\label{fig:specphot1821autoS}
	}
\subfloat[2MASS J1821 - Manual shifting ]{
	\includegraphics[width=0.5\textwidth]{specphot_1821_manual_noremovel.pdf}
	\label{fig:specphot1821manualS}
	}
	\caption{Dynamic spectra of {\shb} using automatic cross correlation wavelength shifting (left) and manual wavelength shifting(right).
	The manual method shows better systematics but higher frequency noise.}
	\label{fig:manualVsAutoShift1821}
	\vspace{0.1in}
\end{figure*} 
%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

>>>>

\begin{figure*}[!t]
\centering
\subfloat[2MASS J1821- Automatic Shifting]{
	\includegraphics[width=0.5\textwidth]{specphot_1821_auto_noremovel.pdf}
	\label{fig:specphot1821autoS}
	}
\subfloat[2MASS J1821 - Manual shifting ]{
	\includegraphics[width=0.5\textwidth]{specphot_1821_manual_noremovel.pdf}
	\label{fig:specphot1821manualS}
	}
	\caption{Dynamic spectra of {\shb} using automatic cross correlation wavelength shifting (left) and manual wavelength shifting(right).
	The manual method shows better systematics but higher frequency noise.}
	\label{fig:manualVsAutoShift1821}
	\vspace{0.1in}
\end{figure*}

\clearpage
\pagebreak
\subsection{MCMC Time Series Fits}

Fitting all light curves to \sha\ with MCMC methods and without the A$_1$ > 0 prior results in more non-detections, but an unusual pattern to the spectra.
As with other MCMC fits, error bars are from photon and read noise, so they're likely under-estimated.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{mcmc_spectrum_2mass_0835.pdf}
\caption{Spectrum of \sha\ using all MCMC fits with 1 cosine term .}\label{fig:mcmcSpec0835}
\end{centering}
\end{figure}

%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.
